Painting with Triangles

### 2014-04-21 paper.tex
foo

Other work has proposed novel vector graphic data structures. For example 
Frisken~\etal~\shortcite{Frisken:2000:ASD:344779.344899}
introduced Adaptively Sampled Distance Fields (ADFs), which specify a signed distance function to a surface in 3D
(or a curve in the plane).
%
Rendering the shape requires sampling the function to determine whether or not a pixel is on the shape.
A quadtree accompanies the distance function to specify where higher sampling rates are necessary. The method of Bremer~\etal~\shortcite{Bremer:2001:VCM}
further describes how ADFs can be created and used. However, it is unclear how ADFs might be used in a general
painting program where strokes with solid colors and gradients are composited on top of one another.

@@

Another series of works have created entirely new ways of painting. Orzan~\etal~\shortcite{Orzan:2008:DCV:1360612.1360691}
specified Diffusion curves which
describe a new painting technique where artists specify edges and colors for those edges. Their system
then solves a Poisson equation to diffuse the colors between boundary conditions specified at the edges.
Similarly the method of McCann and Pollard~\shortcite{McCann:2008:RGP:1360612.1360692}
lets artists paint in the gradient domain. Both of these approaches yield fantastic works of art, yet
they are really new mediums for artists to explore rather than a vectorized version of conventional
painting techniques.

@@

\subsection{Boundary Edges}
Although the triangles may change over time, they must abide by constraints we call
\emph{boundary edges}, each of which connects a pair of points and specifies that no triangle
can cross it. Like mesh points, boundary edges are persistent. 
%
So as new triangles are created by the triangulation algorithm, they
may never cross a boundary edge.  
This partially restricts the set of valid triangulations of the points.  Figure~\ref{fig:stroke} shows boundary edges for a soft brush stroke.

@@

\begin{figure}
    \centering
        \includegraphics[width=0.5\textwidth]{images/gradientarcs}
    \caption{A close look at a gradient stroke. The blue edges are boundaries where
    the points have gray color arcs as shown. The purple edges are boundaries where
    the points have transparent gray color arcs. This gives triangles connecting the two boundaries
    a linear gradient from gray to white.}
    \label{fig:softarcs}
\end{figure}

>>>>

Other work has proposed novel vector graphic data structures. For example 
Frisken~\etal~\shortcite{Frisken:2000:ASD:344779.344899}
introduced Adaptively Sampled Distance Fields (ADFs), which specify a signed distance function to a surface in 3D
(or a curve in the plane).
%
Rendering the shape requires sampling the function to determine whether or not a pixel is on the shape.
A quadtree accompanies the distance function to specify where higher sampling rates are necessary. The method of Bremer~\etal~\shortcite{Bremer:2001:VCM}
further describes how ADFs can be created and used. However, it remains unclear how ADFs might be used in a general
painting program where strokes with solid colors and gradients are composited on top of one another.

@@

Another line of research has explored entirely new ways of painting.
Orzan~\etal~\shortcite{Orzan:2008:DCV:1360612.1360691}
specified Diffusion curves which
describe a new painting technique where artists specify edges and colors for those edges. Their system
then solves a Poisson equation to diffuse the colors between boundary conditions specified at the edges.
Similarly the method of McCann and Pollard~\shortcite{McCann:2008:RGP:1360612.1360692}
lets artists paint in the gradient domain. Both of these approaches yield creative new aesthetic ranges 
beyond what is straightforward in the traditional pixel-based painting model. Nevertheless,
they represent a new painting metaphor for the artist, rather than a vectorized version of the conventional
digital painting approach familiar to artists.

@@

\subsection{Boundary Edges}
Although the triangles may change over time, they must abide by constraints we call
\emph{boundary edges}, each of which connects a pair of points and specifies that no triangle
can cross it. Like mesh points, boundary edges are persistent. 
%
So as new triangles are created by the triangulation algorithm, they
may never cross a boundary edge.  
This partially restricts the set of valid triangulations of the points.  Figure~\ref{fig:stroke} shows boundary edges for a soft  stroke.

\begin{figure}[t]
    \centering
        \includegraphics[width=0.5\textwidth]{images/gradientarcs}
    \caption{A close look at a gradient stroke. The blue edges are boundaries where
    the points have gray color arcs as shown. The purple edges are boundaries where
    the points have transparent gray color arcs. This gives triangles connecting the two boundaries
    a linear gradient from gray to white.}
    \label{fig:softarcs}
\end{figure}

@@
